Special Events

### 2013-07-15 pnsac/jul13/article_ForthEvents.tex
Changes and images for Jul 2013 newsletter.

\begin{tabbing}
May 30, 2013     \hspace{20mm}\= Board of Directors' Meeting\\
 {\normalfont\color{red}June 8, 2013}     \>
 {\normalfont\color{red}Annual General Meeting}\\
June 8, 2013      \> Board of Directors' Meeting (post AGM)\\
June 27, 2013     \> Board of Directors' Meeting (first meeting of new Board)\\
September 12, 2013     \> Board of Directors' Meeting (to be confirmed)\\
September 21, 2013     \> Members' Quarterly Meeting (to be confirmed)\\
November 28, 2013      \> Board of Directors' Meeting (to be confirmed)\\
December 7, 2013       \> Members' Quarterly Meeting (to be confirmed)\\
March 20, 2014         \> Board of Directors' Meeting (to be confirmed)\\
March 29, 2014         \> Members' Quarterly Meeting (to be confirmed)

>>>>

\begin{tabbing}
%May 30, 2013     \hspace{20mm}\= Board of Directors' Meeting\\
% {\normalfont\color{red}June 8, 2013}     \>
% {\normalfont\color{red}Annual General Meeting}\\
%June 8, 2013      \> Board of Directors' Meeting (post AGM)\\
%June 27, 2013     \> Board of Directors' Meeting (first meeting of new Board)\\
September 12, 2013     \hspace{20mm}\= Board of Directors' Meeting (to be confirmed)\\
September 21, 2013     \> Members' Quarterly Meeting (to be confirmed)\\
November 28, 2013      \> Board of Directors' Meeting (to be confirmed)\\
December 7, 2013       \> Members' Quarterly Meeting (to be confirmed)\\
March 20, 2014         \> Board of Directors' Meeting (to be confirmed)\\
March 29, 2014         \> Members' Quarterly Meeting (to be confirmed)

### 2013-07-15 pnsac/jul13/article_SpecialEvents.tex
Changes and images for Jul 2013 newsletter.

\section{Project North Star Visit to RCAF 426 Squadron ``Thunderbirds''
  -- Friday Jun 14, 2013'}
\label{sec:trenton}

Project North Star is pleased to announce a tour of 426 Squadron at
RCAF Trenton on Friday, June 14th, 2013.  This visit came up at very
short notice, through the help of Tim Timmins (retired Colonel CAF and
member of PNSAC) and Lieutenant Colonel Damon Perrault, Commanding
Officer of 426 Squadron.

Due to the fantastic demand that was generated for our trip to
Montreal, I would strongly recommend an early booking to avoid
disappointment as seats are limited for this fun day of activities.

Our visit to 426 Squadron, which does all the training for the new
C-130J, will involve a tour of their brand new state of the art
training facilities that includes the two airframes that are used for
technician training, another airframe for training loadmasters, a
procedure trainer, and full motion simulators with the usual caveat
``operational requirements.''

After our visit, we will attend the RCAF Memorial Museum which has
undergone a major upgrade to its display area along with their work
shops.

Afterwards we will have a debriefing at Rumour's Restaurant for
schnitzel before returning to Ottawa.

The cost per person is \$70:00. Please send two cheques including a
non-refundable deposit of \$30:00 and a post- dated cheque in the
amount of \$40:00 dated May 14, 2013.

Please note ``Trenton Trip'' on your cheques in addition to sending me
(Bill Tatae) an e-mail message (\email{pnsac.specialevents@gmail.com})
to confirm your participation.  Please include your full name and date
of birth in your e-mail message (this is a requirement of RCAF
Security) as well as your preferred contact information, email or
telephone.

Active volunteers can bring your cheques to the PNSAC office at the
CASM or alternatively mail to:

@@

Our Second planned Special Event is for Wednesday August 14th which is
Third Annual Golf Day at Loch March in Carp Ontario.

The day will start off with breakfast at 09:00 with golf starting
shortly after 10:00.

The club professional, as last year, has graciously given PNSAC two
free passes for 18 holes at Loch March, which will be awarded for the
longest drive (staying in bounds of course) and closest to the
pin. Format will be best ball.

Afterwards on the deck, we will discuss the day's game and the
Vice-President will give the winner a ``free beer'' for their effort.

Please email \email{pnsac.specialevents@gmail.com} to confirm you are coming
and call the starter at Loch March 613-839-5885.

Please visit the web site
{\normalfont\color{blue}\texttt{\url{www.lochmarch.com}}} for more
information such as facilities and dress code.

>>>>

@@

\begin{figure}[htbp]
   \vspace{2em}
   \centering
   %name of the graphic, without the path AND in EPS format:
   \includegraphics[scale=1.5]{loch_march.eps}
   %caption of the figure 
   %\caption*{\small \em North Star engine 3.}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:logo}
\end{figure}

A two week break of the restoration of the aircraft will occur in
August, as Mike Irvin takes a well-deserved holiday.

On Wednesday, August 14th, PNSAC will have its third annual golf day
at the beautiful Loch March golf course starting at 10:00 A.M. with a
nine minute separation between flights.  The format for the 18 holes
will be a best ball game.

The club house at Loch March has an excellent breakfast menu so to
make your day more enjoyable it is recommended we meet for breakfast
before the game at 9:00 A.M.

Danielle Nadon, the Club Professional at Loch March has graciously
given us two 18 hole passes for the winner of longest drive and
closest to the pin.

You are encouraged to wear your distinctive PNSAC golf shirt and ball
cap.  As before, guests are welcome.

Please email Danielle at \email{danielle@lochmarch.com} for booking, advising
her that you are part of the Project North Star Day.  Please remember
to send a copy of your e-mail to: \email{pnsac.specialevents@gmail.com}.

Please review the web site\\
{\color{blue}\texttt{\url{http://www.lochmarch.com/about}}} to
familiarize yourself with directions and dress code restrictions to
make your day a ``Great Day at Loch March''.

\begin{itemize}
  \item Seniors mid week rate is \$48:00 and under 60 is \$58:00 plus
    H.S.T
  \item Power cart rental is \$15:49 per person for 18 holes plus
    H.S.T.
  \item Pull cart rental \$5:31 plus H.S.T.
\end{itemize}
